---
title: "Lab 7"
format: html
server: shiny
---

## Lab Overview

This lab will use the Canadian cheese dataset to explore features of Shiny. 

Learn more about Shiny interactive documents at [https://shiny.posit.co](https://shiny.posit.co) and <https://quarto.org/docs/interactive/shiny/>.

### Question 1 (5 points)

Update the default Shiny app to use the cheese dataset to create a histogram using the moisture percentage of the cheeses. Replace the histogram with a ggplot version and input number of bins directly in `geom_histogram()`. Note that you'll need to import data & load libraries within the server code.


```{r}
sliderInput("bins", "Number of bins:", 
            min = 1, max = 50, value = 30)
plotOutput("distPlot")
```

```{r}
#| context: server
output$distPlot <- renderPlot({
  library(tidyverse)
  cheese <- read_csv('https://raw.githubusercontent.com/stat408/Data/refs/heads/main/cheese_data.csv') |>
    filter(!is.na(MoisturePercent))
  
   x <- faithful[, 2]  # Old Faithful Geyser data
   bins <- seq(min(x), max(x), length.out = input$bins + 1)
   hist(x, breaks = bins, col = 'darkgray', border = 'white',
        xlab = 'Waiting time to next eruption (in mins)',
        main = 'Histogram of waiting times')
})
```


## Solution

```{r}
sliderInput("bins1b", "Number of bins:", 
            min = 1, max = 50, value = 30)
plotOutput("distPlot1b")
```

```{r}
#| context: server
output$distPlot1b <- renderPlot({
  library(tidyverse)

  cheese <- read_csv('https://raw.githubusercontent.com/stat408/Data/refs/heads/main/cheese_data.csv') |>
    filter(!is.na(MoisturePercent))
  
  cheese |>
    ggplot(aes(x = MoisturePercent)) +
    geom_histogram(bins = input$bins1b, fill = 'goldenrod') +
    xlab("Moisture Percent of Canadian Cheese") +
    theme_dark()

})
```

---

### Question 2 (5 points)

Explore the control widgets available in shiny [https://shiny.posit.co/r/getstarted/shiny-basics/lesson3/](https://shiny.posit.co/r/getstarted/shiny-basics/lesson3/) and add another widget to your output from the first question.


```{r}
sliderInput("bins", "Number of bins:", 
            min = 1, max = 50, value = 30)
radioButtons("fill_color", "Histogram Color:",
               c("goldenrod" = "goldenrod",
                 "turquoise" = "turquoise",
                 "lavender" = "lavender"))
plotOutput("distPlot2")
```

```{r}
#| context: server
output$distPlot2 <- renderPlot({
  library(tidyverse)

  cheese <- read_csv('https://raw.githubusercontent.com/stat408/Data/refs/heads/main/cheese_data.csv') |>
    filter(!is.na(MoisturePercent))
  
  cheese |>
    ggplot(aes(x = MoisturePercent)) +
    geom_histogram(bins = input$bins, fill = input$fill_color) +
    xlab("Moisture Percent of Canadian Cheese") +
    theme_dark()
})
```

---

### Question 3 (5 points)

Explore the reactive output options in Shiny [https://shiny.posit.co/r/getstarted/shiny-basics/lesson4/](https://shiny.posit.co/r/getstarted/shiny-basics/lesson4/) and add another output

```{r}
sliderInput("bins", "Number of bins:", 
            min = 1, max = 50, value = 30)
radioButtons("fill_color2", "Histogram Color:",
               c("goldenrod" = "goldenrod",
                 "turquoise" = "turquoise",
                 "lavender" = "lavender"))
plotOutput("distPlot3")
textOutput("text")

```

```{r}
#| context: server
output$distPlot3 <- renderPlot({
  library(tidyverse)

  cheese <- read_csv('https://raw.githubusercontent.com/stat408/Data/refs/heads/main/cheese_data.csv') |>
    filter(!is.na(MoisturePercent))
  
  cheese |>
    ggplot(aes(x = MoisturePercent)) +
    geom_histogram(bins = input$bins, fill = input$fill_color2) +
    xlab("Moisture Percent of Canadian Cheese") +
    theme_dark()
})

output$text <- renderText({ paste('You have selected', input$fill_color2, 'as the fill color in the histogram.', sep = ' ') })
```

---

### Question 4 (5 points)

Create a new reactive figure that allows the user to create side-by-side violin plots of `MoisturePercent` by a selected variable. Hint: use `varSelectInput` and see the reference on the main shiny page <https://shiny.posit.co>.

---

```{r q4, message = F}
library(tidyverse)
cheese <- read_csv('https://raw.githubusercontent.com/stat408/Data/refs/heads/main/cheese_data.csv') 

varSelectInput("xvar", "Choose a grouping variable:", cheese |>
                 select(ManufacturerProvCode,
                        ManufacturingTypeEn,
                        CategoryTypeEn,
                        MilkTypeEn,
                        MilkTreatmentTypeEn,
                        RindTypeEn,
                        FatLevel),
               selected = "ManufacturingTypeEn")
plotOutput("violin")

textOutput("text2")

```



```{r}
#| context: server
output$violin <- renderPlot({
  library(tidyverse)
  library(viridis)

 cheese <- read_csv('https://raw.githubusercontent.com/stat408/Data/refs/heads/main/cheese_data.csv') |>
  filter(!is.na(MoisturePercent))
library(viridis)
cheese |>
  ggplot(aes(y = MoisturePercent, x = !!input$xvar, color = !!input$xvar)) +
  theme_bw() +
  scale_color_viridis( discrete =T) +
  geom_violin() +
  geom_jitter() + 
  theme(legend.position = 'none')
})

output$text2 <- renderText({ paste('You have selected', input$xvar, 'as the fill color in the histogram.', sep = ' ') })
```